Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-30 paper.tex
End warning on a more positive note

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular, background selection has been shown to affect genomewide
sequence variation in a wide range of
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}.
Thus care must be taken to ensure that the results of neutral simulations are
appropriate for the question and genomic partition under study.

>>>>

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular, background selection has been shown to affect genomewide
sequence variation in a wide range of
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}.
Thus care must be taken to ensure that the results of purely neutral simulations are
appropriate for the question and genomic partition under study.
A major strength of \msprime\ is that it can be used in conjunction
with forwards-time simulators, enabling the simulation of much
more realistic models than otherwise
possible~\citep{kelleher2018efficient,haller2018tree}.
